An Investigation of Confusing Code Patterns in JavaScript

### 2022-12-14 s02.tex
presenting an overview of the studies
review os s04
remove unused final_ds

\section{Latin Square Study}\label{sec:meth:survey}

This experiment uses a different experimental design that makes it possible to control for the experience of the subjects. It employs a subset of the atom candidates used in the repeated measures study. More specifically, this study investigates ten of the atoms investigated in the repeated measures study: 
%Since JavaScript and \clang have some constructs in common (Section~\ref{back}), we first 
%select a set of 9+1 atom candidates: 
nine previously-validated atoms of confusion for the \clang language~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17} that also exist in JavaScript programs plus one atom candidate that is specific to the JavaScript language (Automatic Semicolon Insertion). 
%Our supplementary material discusses and shows examples of the atoms we consider in our research.\castor{We should probably do this here or just refer to the table that I intend to insert for the replication study.}

@@

 % latex table generated in R 4.0.4 by xtable 1.8-4 package
 % Thu Apr 22 07:58:21 2021
 \begin{table*}[ht]
\caption{Hypotheses Testing (misunderstanding and time). Asterisks ($^{*}$) indicate a statistically significant difference.}
 \centering
 {\scriptsize
 \begin{tabular}{lrrr|rr}
   \toprule
Atom  & Chi-square & Odds          & Confidence & Mann-Whitey& Cliff's\\ 
 &  test &Ratio          & Interval &  U test & Delta \\  \midrule
Comma Operator & \textbf{$<$ 0.0001*} & 19.02 & (6.60, 68.22) & \textbf{$<$ 0.0001*} & -0.53 \\ 
Automatic Semicolon Insertion & \textbf{$<$ 0.0001*} & 39.33 & (9.21, 356.62) & 0.0980 & -0.16 \\ 
Post-Increment & \textbf{0.0015*} & 4.83 & (1.73, 15.74) & 0.1201 & 0.15 \\ 
Omitted Curly Braces & 0.0510 & 2.35 & (1.00, 5.77) & 0.9253 & -0.01 \\ 
Assignment as Value & \textbf{0.0035*} & 8.39 & (1.81, 79.12) & 0.8268 & 0.02 \\ 
Implicit Predicate & \textbf{0.0112*} & 6.95 & (1.46, 66.56) & \textbf{0.0029*} & -0.29 \\ 
Logic as Control Flow & 0.2920 & 1.54 & (0.73, 3.28) & \textbf{$<$ 0.0001*} & -0.39 \\ 
Conditional Operator & 0.1590 & 2.73 & (0.74, 12.57) & 0.2407 & -0.12 \\ 
Pre-Increment & 0.7015 & 1.25 & (0.55, 2.85) & \textbf{0.0062*} & 0.27 \\ 
Arithmetic as Logic & 1 & 0.84 & (0.22, 3.12) & \textbf{0.0172*} & 0.23 \\ 
    \bottomrule
 \end{tabular}}
 \label{tab:hypothesis-testing}
 \end{table*}

>>>>

\section{Latin Square Study}\label{sec:s02}

This study uses a different experimental design that makes it possible to control for the experience of the subjects. It employs a subset of the atom candidates used in the repeated measures study. More specifically, this study investigates ten of the atoms investigated in the repeated measures study: 
%Since JavaScript and \clang have some constructs in common (Section~\ref{back}), we first 
%select a set of 9+1 atom candidates: 
nine previously-validated atoms of confusion for the \clang language~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17} that also exist in JavaScript programs plus one atom candidate that is specific to the JavaScript language (Automatic Semicolon Insertion).  
%Our supplementary material discusses and shows examples of the atoms we consider in our research.\castor{We should probably do this here or just refer to the table that I intend to insert for the replication study.}

@@

 % latex table generated in R 4.0.4 by xtable 1.8-4 package
 % Thu Apr 22 07:58:21 2021
 \begin{table*}[ht]
\caption{Hypotheses Testing (misunderstanding and time). Asterisks ($^{*}$) indicate a statistically significant difference.}
 \centering
 {\scriptsize
 \begin{tabular}{lrrr|rr}
   \toprule
      & \multicolumn{3}{c}{Correcness analysis} & \multicolumn{2}{c}{Time analysis} \\ \toprule
Atom  & Chi-square & Odds           & Confidence & Mann-Whitey& Cliff's\\ 
 &  test &Ratio          & Interval &  U test & Delta \\  \midrule
Comma Operator & \textbf{$<$ 0.0001*} & 19.02 & (6.60, 68.22) & \textbf{$<$ 0.0001*} & -0.53 \\ 
Automatic Semicolon Insertion & \textbf{$<$ 0.0001*} & 39.33 & (9.21, 356.62) & 0.0980 & -0.16 \\ 
Post-Increment & \textbf{0.0015*} & 4.83 & (1.73, 15.74) & 0.1201 & 0.15 \\ 
Omitted Curly Braces & 0.0510 & 2.35 & (1.00, 5.77) & 0.9253 & -0.01 \\ 
Assignment as Value & \textbf{0.0035*} & 8.39 & (1.81, 79.12) & 0.8268 & 0.02 \\ 
Implicit Predicate & \textbf{0.0112*} & 6.95 & (1.46, 66.56) & \textbf{0.0029*} & -0.29 \\ 
Logic as Control Flow & 0.2920 & 1.54 & (0.73, 3.28) & \textbf{$<$ 0.0001*} & -0.39 \\ 
Conditional Operator & 0.1590 & 2.73 & (0.74, 12.57) & 0.2407 & -0.12 \\ 
Pre-Increment & 0.7015 & 1.25 & (0.55, 2.85) & \textbf{0.0062*} & 0.27 \\ 
Arithmetic as Logic & 1 & 0.84 & (0.22, 3.12) & \textbf{0.0172*} & 0.23 \\ 
    \bottomrule
 \end{tabular}}
 \label{tab:hypothesis-testing}
 \end{table*}
